\documentclass[twoside]{article}

\usepackage{ustj}

\newcommand{\authorname}{N. E. Davis}
\newcommand{\authorpatp}{\patp{lagrev-nocfep}}
\newcommand{\affiliation}{Urbit Foundation}

%  Make first page footer:
\fancypagestyle{firststyle}{%
\fancyhf{}% Clear header/footer
\fancyhead{}
\fancyfoot[L]{{\footnotesize
              %% We toggle between these:
              % Manuscript submitted for review.\\
            %   {\it Urbit Systems Technical Journal} I:1 (2024):  1. \\
            %   ~ \\
            %   Address editorial correspondence to \authorpatp.
              }}
}
%  Arrange subsequent pages:
\fancyhf{}
\fancyhead[LE]{{\urbitfont Urbit Systems Technical Journal}}
\fancyhead[RO]{Letter from the Editor}
\fancyfoot[LE,RO]{\thepage}

%%MANUSCRIPT
\title{From the Editor}
\author{\authorname~\authorpatp \\ \affiliation}
\date{}

\begin{document}

%\maketitle
\thispagestyle{firststyle}

% We will adjust page numbering in final editing.
\pagenumbering{arabic}
\setcounter{page}{1}

When I first encountered Urbit, it was like Mr.\ Electrico touching twelve-year-old Ray Bradbury with a charged sword and commanding him to “live forever!”  The vision of unfolding but comprehensible complexity was to me a siren song that has led me into rewarding professional relationships and deep friendships.  This shape rotator programming has become a lifelong passion and fertile ground of exploration.
%Urbit, Nock, and their entailments are a horn of plenty for ambitious computer scientists and developers to draw from.

\sloppy
This issue of the \emph{Urbit Systems Technical Journal} unveils technical descriptions of significant milestones in Urbit's ongoing development.  \patp{rovnys-ricfer}, \patp{master-morzod}, \patp{watter-parter}, \patp{dinleb-rambep}, \patp{norsyr-torryn}, and \patp{hastuc-dibtux} detail the design and implementation of Urbit's named data networking scheme, Directed Messaging, a core component of the 2023 ``Neo-Urbit'' vision.  \patp{dozreg-toplud} expounds the long-anticipated ``subject knowledge analysis'' paradigm for Hoon static analysis, proposed several years ago by \patp{ritpub-sipsyl} and long a target for more efficient Hoon compilation to the Nock combinator calculus.  \patp{hanfel-dovned} presents portions of the Groundwire proposal for a revision of Urbit's peer-to-peer schema beyond Azimuth, a topic of ongoing technical interest in the Urbit developer community.  \patp{ticlys-monlun} and \patp{lagrev-nocfep} explain how the Nock serialization mechanism for nouns works in detail.  And \patp{nomryg-nilref} reveals in great detail his monumental labor of love that is Obelisk, a return to E.\ F.\ Codd’s relational algebra and \textsc{sql}.  Each article represents years of design and engineering work, and we are proud to present them to the Urbit community.

As of 2025, \emph{USTJ} has become a sponsored product of the Groundwire Foundation, a new nonprofit entity dedicated to Urbit's core development and improving support for Bitcoin integrations into the Urbit ecosystem.

Computer science happens in the trenches.  \tombstone{}
\end{document}

% Issue 2:  
% Exit the only game in town.
